学術論文

### 2022-04-06 articles.Rmd
update

>>>>

- [39] Psychological Science Accelerator Self-Determination Theory Collaboration (in press). A global experiment on motivating social distancing during the COVID-19 pandemic. Proceedings of the National Academy of Sciences. DOI: 10.31234/osf.io/n3dyf

- [38] Somatori, K. & Kunisato, Y. (in press) Metacognitive Ability and the Precision of Confidence. Frontiers in Human Neuroscience, section Cognitive Neuroscience [Link](https://www.frontiersin.org/articles/10.3389/fnhum.2022.706538/abstract)
